---
title: "WorldDevelopmentSlides"
author: "Max Jiang"
date: "2024-10-07"
format: revealjs
  theme: night  
  transition: slide  
editor: visual
---

## 

# Introduction to World Development Indicators

We will explore key socioeconomic indicators such as GDP per capita, life expectancy, and total population.

## 

# Summary of Key Findings

-   GDP per capita varies significantly across countries.
-   Life expectancy is positively correlated with GDP per capita.

## 

# Density Plot of GDP Per Capita

```{r}
#| echo: false
#| fig-cap: "Density Plot of GDP Per Capita"
ggplot(indicators, aes(x = gdp_per_capita)) +
  geom_density(fill = "lightblue", alpha = 0.7) +
  labs(title = "Density Plot of GDP Per Capita", x = "GDP Per Capita", y = "Density") +
  theme_minimal()
```

# Scatter Plot: Life Expectancy vs GDP Per Capita

```{r}
#| echo: false
#| fig-cap: "Scatter Plot of Life Expectancy vs GDP Per Capita"
ggplot(indicators, aes(x = gdp_per_capita, y = life_expectancy)) +
  geom_point(color='purple') +
  labs(title = "Life Expectancy vs GDP Per Capita", x = "GDP Per Capita", y = "Life Expectancy") +
  theme_minimal()
```

# Conclusion

Our analysis highlights disparities in GDP per capita and life expectancy across different countries.
